Structural Causal Models - A Gentle Introduction

### 2021-04-19 draft.Rmd
different actions
draft

---
title: "draft"
author: "Daniel Saggau"
date: "4/19/2021"
output: pdf_document
---

@@

##

@@

>>>>

---
title: "Structural Causal Models - A Gentle Introduction"
author: 
- Daniel Saggau $\boldsymbol{\cdot}$ `daniel.saggau@campus.lmu.de`
- Department of Statistics, Ludwig Maximilian University Munich, Germany
date: "April 2021"
output: 
  pdf_document: 
    number_sections: yes
    fig_caption: yes
citation_package: --biblatex
fontsize: 12
linestretch: 1.5
---

@@

@@

 |Method          | Action |  Example
|-----------------|---------------------------|------------------------|
| Prediction      | Observation/Co-occurrence | What happened...
| Intervention    | Do-manipulation           | What happens if ...
| Counterfactual  | Hypothetical Realities    | What would have happened if...

Table: Pearl - Hierachy of Causation
